---
title: "Homework2"
author: "Brian Pennington"
date: "October 12, 2016"
output:
  pdf_document: default
  html_document: default
---
```{r}
library('rcfss')
library("dplyr")
library("ggplot2")
library("tidyverse")
data(gun_deaths)

```

## Part 1

### In what month do the most gun deaths occur?
Grouped by Month and then counted each month
```{r}
gun_deaths %>%
  group_by(month)%>%
  count()
```
we grouped the data by columns and
counted how many gun deaths there were for each month

July has the most gun deaths out of each month



Ran a simple bar graph to visualize results 

```{r}
ggplot(by_month,
       aes(month)) +
  geom_bar() +
  coord_cartesian(xlim = c(1,12), ylim = c(6800, 9200))
```

### What is the most common intent in gun deaths? Do most people killed by guns die in suicides,homicides, or accidental shootings?
```{r}
group_intent = gun_deaths %>%
  group_by(intent) %>%
  count()
group_intent
```
The intent is overwhelmingly towards suicide

```{r}
gun_deaths %>%
  ggplot(aes(intent, fill= intent)) +
  geom_bar()
```

### What is the average age of females killed by guns?
```{r}
female.victims <- filter(gun_deaths, sex == "F") 
summarise(female.victims, mean(age, na.rm = TRUE))
summarise(female.victims, median(age, na.rm = TRUE))


ggplot(female.victims) +
  geom_histogram(aes(age), binwidth = 10)
```

### How many white males with at least a high school education were killed by guns in 2012?

```{r}
gun_deaths %>%   
  select(education, race, year, sex) %>% 
  filter(sex == "M") %>% #filtered by males
  filter(race == "White") %>% #filtered by white
  filter(year == "2012") %>% #filtered for the year 2012
  filter(education == "HS/GED" | education == "BA+") %>% #filtered for education between HS and college+
  summarise(n())
```
counted how many were in the data`
10,941

### Which season of the year has the most gun deaths?

```{r}
gun_deaths %>%
  select(month) %>%
  mutate(seasons = cut(month, #created new varialbe called seasons
                       breaks = c(0, 3, 6, 9, 12), #months between these breaks were then placed into
                       labels = c("Winter", "Spring", "Summer", "Fall")))%>% #these categories
  ggplot(aes(x = seasons)) +
  geom_bar()
```

summer


### What is the relationship between race and intent?

```{r}
gun_deaths %>%
 count(race, intent) #gave the frequencies of race and intent
ggplot(gun_deaths,aes(race, fill = intent)) +
  geom_bar(position = 'dodge')
```
Whites are more likely to utilize guns for suicide, 
whereas blacks use guns more for homicide.
Hispanics seem to use guns more for homicide, as well


## Part 2
```{r}
data(dadmom)
dadmom%>%
  unite(d, named, incd, sep = "_") %>%
  unite(m, namem, incm, sep = "_") %>% #decided to unite before gathering and separating because it made it easier to separate d and m
  gather(d, m, key = "key", value= "value") %>%
  separate(value, into = c("name", "income"), sep = "_") %>%
#gathered so we could separate it into name and income  
  arrange(desc(income))
#arranged it by descending income so it would be easier to read
```


## Part 3

```{r}
court1 <- read.csv("data/SCDB_01.csv")
court2 <- read.csv("data/SCDB_03.csv")
courtdata <- bind_rows(court2, court1)
```


### 1

```{r}
courtdata%>%
  select(term, majVotes, minVotes) %>%
  mutate("votedif" = majVotes - minVotes == 1) %>% #created a dummy
  group_by(term, votedif) %>%
  summarise(n = n()) %>%
  group_by(term)%>% #get rid of voted if
  mutate(npercent = n/sum(n))%>%
  filter(votedif == "TRUE") #filtered to see true split decision
```

## 2

```{r}
courtdata%>%
  select(justiceName, majority) %>%
  mutate("majority" = majority - 1) %>%
  group_by(justiceName, majority) %>%
  summarise(n = n()) %>%
  group_by(justiceName)%>%
  mutate(npercent = n/sum(n))%>%
  filter(justiceName == "AScalia")
```

82% of Scalia's vote were in the majority

## 3

```{r}
courtdata%>%
  select(term, direction) %>% 
  mutate("direction" = direction - 1) %>%
  group_by(term, direction) %>%
  summarise(n = n()) %>%
  group_by(term)%>%
  mutate(npercent = n/sum(n)) %>%
  filter(direction == "0")
```

