---
title: "Write Up"
author: "Brian Pennington"
date: "November 23, 2016"
output: html_document
---
#Introduction
With the recent election of Donald Trump on November 8th, much of populace is looking back to the polsters and news outlets for an explanation. Many polls, including Project 538, had Clinton leading significatly in electoral vote and winning the popular vote. Only half of this prediction has come true. The outcome has prompted many researchers and news outlets to try and provide their own explanation as to what happened. According to a number of these explanations, there is a consensus of Hillary's inability to reach blue collar white males, and actually ostraczing this particularly large voting block. In this analysis, we attempt to dissect the speeches of those who ran for the White House, in order to understand if there was something in the rheotric of the candidates that can explain the outcome. For this particular portion, we look to see if certain words within a given speech predicts the candidate. This should present those words that are almost synonmus with that candidate. We believe that certain cadidates have a prclivity towards particular words lending itself to a particular rhetoric. 

#Methods
For this analysis, we used the candidates speeches they gave prior to Summer of 2015. This gives an opportunity to exaimine candidates rhetoric campaigning through both the primaires and national election. We acquired the speeches through the American Presidency Project (http://www.presidency.ucsb.edu/index.php). 
We ran a random forest analysis in order to randomly generate a number of decision trees, and then compared those decision trees in order to get a robust model. We also attempted to predict whether a particular sentiment could predicate a given candidate using the same methods.

Getting the Data
```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(rvest)
library(stringr)
library(caret)
library(randomForest)
library(tm)
library(knitr)
library(tree)
library(feather)


get_Clinton_speeches <- function(x, y){
  df1 <- read_html(x) %>%
    html_nodes("p") %>%
    html_text()
  
  df2 <- read_html(x)%>%
    html_node(".docdate")%>%
    html_text()
  
  
  speech <- data_frame(text = df1) %>%
    mutate(author = "Clinton",
           docnumber = y,
           parnumber = row_number(),
           date = df2) %>%
    separate(date, into = c("day/month", "year"), sep = ",")
  speech <- unnest_tokens(speech, word, text, token = "words")  
  return(speech)
}  

?spread

#2016 Clinton Presidential Campaign Speeches
#Clinton1 is Nov 3, 2016 - Clinton31 is Dec 15, 2015 
Clinton1 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119498", "1")
Clinton2 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119502", "2")
Clinton3 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119501", "3")
Clinton4 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119500", "4")
Clinton5 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119499", "5")
Clinton6 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119497", "6")
Clinton7 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119157", "7")
Clinton8 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119156", "8")
Clinton9 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119155", "9")
Clinton10 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119154", "10")
Clinton11 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119153", "11")
Clinton12 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119152", "12")
Clinton13 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119151", "13")
Clinton14 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119150", "14")
Clinton15 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119149", "15")
Clinton16 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119164", "16")
Clinton17 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119163", "17")
Clinton18 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119162", "18")
Clinton19 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119161", "19")
Clinton20 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119160", "20")
Clinton21 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119159", "21")
Clinton22 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119158", "22")
Clinton23 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119148", "23")
Clinton24 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=118051", "24")
Clinton25 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119295", "25")
Clinton26 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=116600", "26")
Clinton27 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=111596", "27")
Clinton28 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=111439", "28")
Clinton29 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=111414", "29")
Clinton30 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=111415", "30")
Clinton31 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119292", "31")
Clinton32 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=111418", "32")
Clinton33 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=111419", "33")
Clinton34 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=110267", "34")
Clinton35 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=110269", "35")
Clinton36 <- get_Clinton_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=110268", "36")

Clinton_Corpus <- bind_rows(Clinton1, Clinton2, Clinton3, Clinton4, Clinton5, Clinton6, Clinton7, Clinton8, Clinton9, Clinton10, Clinton11, Clinton12, Clinton13, Clinton14, Clinton15, Clinton16, Clinton17, Clinton18, Clinton19, Clinton20, Clinton21, Clinton22, Clinton23, Clinton24, Clinton25, Clinton26, Clinton27, Clinton28, Clinton29, Clinton30, Clinton31, Clinton32, Clinton33, Clinton34, Clinton35, Clinton36)

get_speeches <- function(x, y, z){
  df1 <- read_html(x) %>%
    html_nodes("p") %>%
    html_text()
  
  df2 <- read_html(x)%>%
    html_node(".docdate")%>%
    html_text()
  
  speech <- data_frame(text = df1) %>%
    mutate(author = y,
           docnumber = z,
           parnumber = row_number(),
           date = df2) %>%
    separate(date, into = c("day/month", "year"), sep = ",")
  speech <- unnest_tokens(speech, word, text, token = "words")  
  return(speech)
}  

#2016 Sanders Presidential Campaign Speeches
Sanders1 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=118045", "Sanders", "1")
Sanders2 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117194", "Sanders", "2")
Sanders3 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117513", "Sanders", "3")
Sanders4 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=116694", "Sanders", "4")
Sanders5 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117516", "Sanders", "5")
Sanders6 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117511", "Sanders", "6")
Sanders7 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=111440", "Sanders", "7")
Sanders8 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117514", "Sanders", "8")
Sanders9 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117512", "Sanders", "9")
Sanders10 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=114496", "Sanders", "10")
Sanders11 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=114487", "Sanders", "11")
Sanders12 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117517", "Sanders", "12")
Sanders13 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=114493", "Sanders", "13")
Sanders14 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=114491", "Sanders", "14")
Sanders15 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=114486", "Sanders", "15")
Sanders16 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=114488", "Sanders", "16")
Sanders17 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=114494", "Sanders", "17")

Sanders_Corpus <- bind_rows(Sanders1,  Sanders2, Sanders3, Sanders4, Sanders5, Sanders6, Sanders7, Sanders8, Sanders9, Sanders10, Sanders11, Sanders12, Sanders13, Sanders14, Sanders15, Sanders16, Sanders17)

get_Trump_speeches <- function(x, y){
  df1 <- read_html(x) %>%
    html_nodes("p") %>%
    html_text()
  
  df2 <- read_html(x)%>%
    html_node(".docdate")%>%
    html_text()
  
  
  speech <- data_frame(text = df1) %>%
    mutate(author = "Trump",
           docnumber = y,
           parnumber = row_number(),
           date = df2) %>%
    separate(date, into = c("day/month", "year"), sep = ",")
  speech <- unnest_tokens(speech, word, text, token = "words")  
  return(speech)
}  

Trump1 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119182", "1")
Trump2 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119181", "2")
Trump3 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119188", "3")
Trump4 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119187", "4")
Trump5 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119186", "5")
Trump6 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119185", "6")
Trump7 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119184", "7")
Trump8 <- get_Trump_speeches('http://www.presidency.ucsb.edu/ws/index.php?pid=119183', "8")
Trump9 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119174", "9")
Trump10 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119172", "10")
Trump11 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119180", "11")
Trump12 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119173", "12")
Trump13 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119170", "13")
Trump14 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119169", "14")
Trump15 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119168", "15")
Trump16 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119167", "16")
Trump17 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119166", "17")
Trump18 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119179", "18")
Trump19 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119202", "19")
Trump20 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119201", "20")
Trump21 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119200", "21")
Trump22 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119203", "22")
Trump23 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119191", "23")
Trump24 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119189", "24")
Trump25 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119192", "25")
Trump26 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119207", "26")
Trump27 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119208", "27")
Trump28 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119209", "28")
Trump29 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119190", "29")
Trump30 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119206", "30")
Trump31 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119206", "31")
Trump32 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119193", "32")
Trump33 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119205", "33")
Trump34 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119178", "34")
Trump35 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119204", "35")
Trump36 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119194", "36")
Trump37 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119195", "37")
Trump38 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119177", "38")
Trump39 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119197", "39")
Trump40 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119199", "40")
Trump41 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119198", "41")
Trump42 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119196", "42")
Trump43 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119176", "43")
Trump44 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119175", "44")
Trump45 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119165", "45")
Trump46 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=119503", "46")
Trump47 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117935", "47")
Trump48 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117791", "48")
Trump49 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117815", "49")
Trump50 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117790", "50")
Trump51 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117775", "51")
Trump52 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117813", "52")
Trump53 <- get_Trump_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=116597", "53")

Trump_Corpus <- bind_rows(Trump1, Trump2, Trump3, Trump4, Trump5, Trump6, Trump7, Trump8, Trump9, Trump10, Trump11, Trump12, Trump13, Trump14, Trump15, Trump16, Trump17, Trump18, Trump19, Trump20, Trump21, Trump22, Trump23, Trump24, Trump25, Trump26, Trump27, Trump28, Trump29, Trump30, Trump31, Trump32, Trump33, Trump34, Trump35, Trump36, Trump37, Trump38, Trump39, Trump40, Trump41, Trump42, Trump42, Trump43, Trump44, Trump45, Trump46, Trump47, Trump48, Trump49, Trump50, Trump51, Trump52, Trump53)

Cruz1 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=118041", "Cruz", "1")
Cruz2 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=117232", "Cruz", "2")
Cruz3 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=116598", "Cruz", "3")
Cruz4 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=114768", "Cruz", "4")
Rubio1 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=111441", "Rubio", "5")
Kasich1 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=116599", "Kasich", "6")
Kasich2 <- get_speeches("http://www.presidency.ucsb.edu/ws/index.php?pid=113069", "Kasich", "7")

Repub_Corpus <- bind_rows(Cruz1, Cruz2, Cruz3, Cruz4, Rubio1, Kasich1, Kasich2)


Total_Corpus <- bind_rows(Clinton_Corpus, Sanders_Corpus, Trump_Corpus, Repub_Corpus)

write_feather(Total_Corpus, "TotalCorpus")
```

Modeling

```{r}

read_feather("TotalCorpus")

corpus_forest <- Total_Corpus %>%
  group_by(author, docnumber) %>%
  count(word) %>%
  select(author, word, n, docnumber) %>%
  mutate(docid = paste0(author, docnumber))
corpus_forest

speech_dtm <- cast_dtm(corpus_forest, term = word, value = n, document = docid)

author_doc <- corpus_forest %>%
  select(author, docnumber) %>%
  unique()
author_doc

aw_forest <- train(y = author_doc$author, x = as.matrix(speech_dtm),
                   method = "rf",
                   ntree = 200,
                   trControl = trainControl(method = "oob"))

aw_forest

str(aw_forest, max.level = 1)
aw_forest$finalModel

kable(aw_forest$finalModel$confusion)

getTree(aw_forest$finalModel, labelVar = TRUE)

varImpPlot(aw_forest$finalModel)


write_feather(corpus_forest, "forestdataframe")
```

I am not sure if this is going to be a correct interpretation of the data. Yet, it seems that our model is fairly accurate and only misses predictions about 1 in 5 times. However, I do believe that this is due to the asymmetry in our sample. If we were to solely predict words based on the probability of author given the number of ducoments by that author, we would have a fairly decent predictor. I believe what is interesting is that for Sanders, the program had the most errors. I beleve that this is due to Sanders having similiairty in rhetoric between both Clinton and Trump. The same can be seen in the sentiment predictions below. We also see that for each tree the program needed to split off about 151 times meaning that not neccessarily a given word predicts speaker, but groups of words. Moving forward, we could examine n-grams as oppsoed to single word to see if n-grams are more accurate.

```{r}
read_feather("TotalCorpus")


Corpus_Sent <- Total_Corpus %>%
  inner_join(get_sentiments("nrc"))

Corpus_Sent <- Corpus_Sent %>%
  group_by(author, docnumber) %>%
  count(sentiment)
Corpus_Sent


sentiment_forest <- Corpus_Sent %>%
  select(author, sentiment, n, docnumber) %>%
  mutate(docid = paste0(author, docnumber))
sentiment_forest

sentiment_dtm <- cast_dtm(sentiment_forest, term = sentiment, value = n, document = docid)
sentiment_dtm

author_doc_2 <- sentiment_forest %>%
  select(author, docnumber) %>%
  unique()
author_doc2

as_forest <- train(y = author_doc_2$author, x = as.matrix(sentiment_dtm),
                   method = "rf",
                   ntree = 200,
                   trControl = trainControl(method = "oob"))
as_forest

str(as_forest, max.level = 1)
as_forest$finalModel

kable(as_forest$finalModel$confusion)

getTree(as_forest$finalModel, labelVar = TRUE)

varImpPlot(as_forest$finalModel)
```

This predictor is a bit worse making about 1 in 3 mistakes. 

We used random forests as opposed to logisitic regression due to the fact that we have many variables than observations. 

Moving forward, we could split the training and test sets in order to compare and have a better judgment of how well the model performs. 