---
title: "HW06"
author: "Brian Pennington"
date: "November 9, 2016"
output: html_document
---
Part 1
Libraries
```{r}

library(geonames) 
library(tidyverse)
library(knitr)
library(gapminder)
library(countrycode)
getOption("geonamesUsername")
```

Pulling data from GeoNames
```{r}
countryInfo <- GNcountryInfo()

countryInfo %>%
  tbl_df()%>%
  head()
```

Data was pulled in as characters
Need to transform to numbers
```{r}
countryInfo <- countryInfo %>%
  transform(areaInSqKm = as.numeric(areaInSqKm))
```

Need to combine GeoNames with Gapminders
Create the Population Density Variable
```{r}
fulldata <- gapminder %>%
  mutate(countryCode = countrycode(gapminder$country, "country.name", "iso2c")) %>%
  left_join(countryInfo[2:17]) %>%
  mutate(popden = pop/areaInSqKm)
```

Redone Graph
```{r, echo= FALSE}
ggplot(aes(popden, lifeExp)) +
  geom_point(alpha = .2) +
  geom_smooth() +
  scale_x_log10() +
  labs(title = "As population  density increases, life expectancy increases",
       x = "Population Density",
       y = "Average life expectancy")
```



Part 2

Pulling necessary libraries and getting up API URL
```{r}
library(tidyverse)
library(httr)
library(stringr)
library(knitr)
library(curl)
library(purrr)

spotifyalbumURL <- "https://api.spotify.com/v1/artists/"
spotifyalbumsongsURL <- "https://api.spotify.com/v1/albums/{id}/tracks"
```

Pulling the data and assignig to its corresponding artist
Save it as a single file (may not be the best way to do it)
These are the top 20 artists for 2016 according to Billboard
(http://www.billboard.com/artists/top-100?page=1)
```{r}
billboard20 <- data.frame(
  drake  = "https://play.spotify.com/artist/3TVXtAsR1Inumwj472S9r4",
  justin_bieber = "https://play.spotify.com/artist/1uNFoZAHBGtllmzznpCI3s", 
  twentyone_pilots = "https://play.spotify.com/artist/3YQKmKGau1PzlVlkL1iodx",
  chainsmokers ="https://play.spotify.com/artist/69GGBxA162lTqCwzJG5jLp", 
  rihanna = "https://play.spotify.com/artist/5pKCCKE2ajJHZ9KAiaK11H",
  adele = "https://play.spotify.com/artist/4dpARuHxo51G3z768sgnrY",
  shawn_mendes = "https://play.spotify.com/artist/7n2wHs1TKAczGzO7Dd2rGr",
  arianna_grande = "https://play.spotify.com/artist/66CXWjxzNUsdJxJ2JdwvnR",
  desiigner = "https://play.spotify.com/artist/7pFeBzX627ff0VnN6bxPR4",
  future = "https://play.spotify.com/artist/1RyvyyTE3xzB2ZywiAwp0i",
  bryson_tiller = "https://play.spotify.com/artist/2EMAnMvWE2eb56ToJVfCWs",
  fifth_harmony = "https://play.spotify.com/artist/1l8Fu6IkuTP0U5QetQJ5Xt",
  the_weekend = "https://play.spotify.com/artist/1Xyo4u8uXC1ZmMpatF05PJ",
  meghan_trainor = "https://play.spotify.com/artist/6JL8zeS1NmiOftqZTRgdTz", 
  sia = "https://play.spotify.com/artist/5WUlDfRSoLAfcVSX1WnrxN", 
  mike_posner = "https://play.spotify.com/artist/2KsP6tYLJlTBvSUxnwlVWa", 
  calvin_harris = "https://play.spotify.com/artist/7CajNmpbOovFoOoasH2HaY", 
  selena_gomez = "https://play.spotify.com/artist/0C8ZW7ezQVs4URX5aX7Kqx", 
  dnce = "https://play.spotify.com/artist/6T5tfhQCknKG4UnH90qGnz",
  charlie_puth = "https://play.spotify.com/artist/6VuMaDnrHyPL1p4EHjYLi7")
```

Need to mutate the URLs in order to pull the Spotify ID
Then use the new API URL to pull data from Spotify
```{r}
billboard20 <- billboard20 %>%
  gather("artists", "links") %>%
  mutate(id = substring(links, 33)) %>% 
  mutate(APIURL = str_c(spotifyalbumURL, id, "/albums"))
```

Dr. Soltoff's code to unnest

 get results using jsonlite
```{r}
results <- map(billboard20$APIURL, fromJSON, flatten = TRUE)
```
  the json response from Spotify has lots of unnecessary info
  we only want to keep the element called "items" from the original
  response
```{r}
results_clean <- vector("list", length(results))
for(artist in seq_along(results)){
  results_clean[[artist]] <- results[[artist]]$items
}
```
  the data is still not very clean - lets combine all the results into a single data frame
  and fix the artists column - currently it is stored as a list-column
```{r}
results_clean <- results_clean %>%
  bind_rows() %>%
  tbl_df() %>%
  unnest(artists)
```

I need to rename columns due to replication in column names
Here is how far I got
```{r}
variablenum = c(1:13)
results_varnum = rbind(results_clean, variablenum)
```
Possibly using a split function here may help
If I were to continue, I would need to get rid of the duplicate observations which would be tricky as well. 